---
title: "p8105_hw3_sz3030"
author: "Shaocong Zhang"
date: "10/18/2021"
output: github_document
---
# Problem 1

## Load the dataset

```{r}
library(tidyverse)
library(ggridges)
library(p8105.datasets)
data("instacart")
```

The dataset has `r nrow(instacart)` rows and `r ncol(instacart)` columns. The 15 variables include different kinds of order, product and user id information, aisles' id and their information and product names extra. 

```{r}
instacart %>%
  group_by(aisle) %>%
  count() %>%
  arrange(n)
```
As this is a 134 x 2 tibble, then there are 134 aisles here and "fresh vegetables" and "fresh fruits" aisles are the most items ordered from.

## Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
instacart %>%
  count(aisle) %>%
  filter(n > 10000) %>%
  mutate(aisle = fct_reorder(aisle, n)) %>% 
  ggplot(aes(x = aisle, y = n)) + 
  geom_point() +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  labs(
    title = "Aisles with more than 10000 items ordered" ,
    x = "Aisles" ,
    y = "Order numbers"
  )


```

## Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart %>%
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  group_by(aisle) %>%
  count(product_name) %>%
  mutate(pop_rank = min_rank(desc(n))) %>%
  filter(pop_rank < 4) %>%
  arrange(desc(n)) %>%
  knitr::kable()
```

## Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table)

```{r}
instacart %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
  summarize(
    mean_hour_of_day = mean(order_hour_of_day)
  ) %>%
  mutate(order_dow = recode_factor(order_dow, '0' = '7',
                                     '1' = '1', '2' = '2', '3' = '3', '4' = '4', '5' = '5', '6' = '6')) %>%
  pivot_wider(names_from = order_dow, values_from = mean_hour_of_day) %>%
  knitr::kable()
```






