---
title: "p8105_hw3_sz3030"
author: "Shaocong Zhang"
date: "10/18/2021"
output: github_document
---
# Problem 1

## Load the dataset

```{r}
library(tidyverse)
library(ggridges)
library(p8105.datasets)
data("instacart")
```

The dataset has `r nrow(instacart)` rows and `r ncol(instacart)` columns. The 15 variables include different kinds of order, product and user id information, aisles' id and their information and product names extra. 

```{r}
instacart %>%
  group_by(aisle) %>%
  count() %>%
  arrange(n)
```
As this is a 134 x 2 tibble, then there are 134 aisles here and "fresh vegetables" and "fresh fruits" aisles are the most items ordered from.

## Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
instacart %>%
  count(aisle) %>%
  filter(n > 10000) %>%
  mutate(aisle = fct_reorder(aisle, n)) %>% 
  ggplot(aes(x = aisle, y = n)) + 
  geom_point() +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, hjust = 0.5)) +
  labs(
    title = "Aisles with more than 10000 items ordered" ,
    x = "Aisles" ,
    y = "Order numbers"
  )


```

## Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart %>%
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  group_by(aisle) %>%
  count(product_name) %>%
  mutate(pop_rank = min_rank(desc(n))) %>%
  filter(pop_rank < 4) %>%
  arrange(desc(n)) %>%
  knitr::kable()
```

## Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table)

```{r}
instacart %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
  summarize(
    mean_hour_of_day = mean(order_hour_of_day)
  ) %>%
  mutate(order_dow = recode_factor(order_dow, '0' = '7',
                                     '1' = '1', '2' = '2', '3' = '3', '4' = '4', '5' = '5', '6' = '6')) %>%
  pivot_wider(names_from = order_dow, values_from = mean_hour_of_day) %>%
  knitr::kable()
```

# Problem 2

## Load the dataset

```{r}
data("brfss_smart2010")
```

The dataset has `r nrow(brfss_smart2010)` rows and `r ncol(brfss_smart2010)` columns. The 23 variables contain information on lcoation, topic, question, response, and response number. 

## First, do some data cleaning:

```{r}
brfss_smart2010 = 
  brfss_smart2010 %>%
  janitor::clean_names() %>% 
  filter(topic == "Overall Health",
         response %in% c("Excellent", "Very good", "Good", "Fair", "Poor")) %>%
  mutate(response = factor(response, levels = c("Poor", "Fair", "Good", "Very good", "Excellent")))
```

## In 2002, which states were observed at 7 or more locations? What about in 2010?

```{r}
# In 2002
brfss_2002 =
  brfss_smart2010 %>%
  filter(year == 2002) %>%
  group_by(locationabbr, locationdesc) %>%
  distinct(locationabbr) %>%
  group_by(locationabbr) %>%
  summarize(n_locations = n()) %>% 
  filter(n_locations >= 7) %>%
  arrange(n_locations)

brfss_2002
```

```{r}
# In 2010
brfss_2010 =
  brfss_smart2010 %>%
  filter(year == 2010) %>%
  group_by(locationabbr, locationdesc) %>%
  distinct(locationabbr) %>%
  group_by(locationabbr) %>%
  summarize(n_locations = n()) %>% 
  filter(n_locations >= 7) %>%
  arrange(n_locations)

brfss_2010
```

## Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r}
brfss_smart2010 %>%
  filter(response == "Excellent") %>%
  select(year, locationabbr, data_value) %>%
  group_by(year, locationabbr) %>%
  summarise(avg_data_value = mean(data_value)) %>%
  ggplot(aes(x = year, y = avg_data_value, group = locationabbr, color = locationabbr)) +
  geom_line() +
  labs(
    x = "Year",
    y = "Average of the data values"
  )
```


## Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

```{r}
brfss_smart2010 %>%
  filter(year %in% c(2006, 2010)) %>%
  group_by(response, data_value) %>%
  filter(locationabbr == "NY") %>%
  ggplot(aes(x = response, y = data_value)) +
  geom_violin(aes(fill = response), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom") +
  labs(
    x = "Response",
    y = "Data value"
  ) +
  facet_grid(~year)


```

# Problem 3

##  Load, tidy, and otherwise wrangle the data.

```{r}
accel_data = 
  read.csv("./accel_data.csv") %>%
  janitor::clean_names() %>%
  pivot_longer(
    activity_1:activity_1440,
    names_prefix = "activity_",
    names_to = "minutes",
    values_to = "counts"
  ) %>%
  mutate(
    minutes = as.numeric(minutes),
    day = as.factor(day),
    day = factor(day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")),
    weekday.vs.weekend = recode(day, "Monday" = "Weekday", "Tuesday" = "Weekday", "Wednesday" = "Weekday", 
                                "Thursday" = "Weekday", "Friday" = "Weekday", "Saturday" = "Weekend",
                                "Sunday" = "Weekend")
  )
```

There are `r nrow(accel_data)` rows and `r ncol(accel_data)` columns in the tidied dataset. There are 6 variables include week number, day id, day(Monday to Sunday), activities and their time and an indicator variable weekday or weekend.

## Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?

```{r}
accel_data %>%
  group_by(week, day) %>%
  summarise(total_counts = sum(counts)) %>%
  pivot_wider(
    names_from = "day",
    values_from = "total_counts"
  )
```

Based on the table, we can conclude that the activity counts for Saturday in week 4 and 5 are the lowest, which show such big gaps between the numbers we get in week 1, 2 and 3 on Saturday. This is because there are lots of "1" count in the original table. What's more, the numbers on weekends usually lower than weekdays.

## Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week.

```{r}
accel_data %>%
  ggplot(aes(x = minutes, y = counts, group = day, color = day)) +
  geom_line(alpha = .5)
```

The count numbers each day are relatively have the same trend throughout the week except in the 1250 minutes of the day. At this time period, we can see big differences between the days. Noted that Sunday is special and having high count numbers at around 650 minutes of the day.


